Status and Best Practices for Reproducible Research In Plant Pathology

### 2017-08-15 inst/paper/Sparks_et_al-main_text.Rmd
Clean up files in /inst/paper directory and use flatly theme in html output
Also

- Drop md intermediate output when generating PDF, no need with HTML,
the HTML renders better, will link to HTML file using raw.github.com to
display the paper online from the README.md file

---
title: "Status and Best Practices for Reproducible Research In Plant Pathology"
author: "A. H. Sparks, E. M. Del Ponte, N. J. Grünwald, and Z. Foster"
date: 'Last update: `r Sys.Date()`'
output:
  word_document:
    keep_md: yes
    reference_docx: Phytopathology_Style_Reference.docx
  pdf_document: default
  html_document: default
csl: phytopathology.csl
bibliography: bibliography.bib
always_allow_html: yes
---

>>>>

---
title: "Status and Best Practices for Reproducible Research In Plant Pathology"
author: "A. H. Sparks, E. M. Del Ponte, N. J. Grünwald, and Z. Foster"
date: 'Last update: `r Sys.Date()`'
output:
  html_document:
    css: my-style.css
    theme: flatly
    toc: true
    toc_float: 
     collapsed: true
     smooth_scroll: true
  pdf_document: default
  word_document:
    reference_docx: Phytopathology_Style_Reference.docx
csl: phytopathology.csl
bibliography: bibliography.bib
always_allow_html: yes
---
